Fig3

### 2020-03-02 analysis/figure-3.Rmd
new fig 3

```{r data}
# pca
charpca <- subsetmakepca(tissuelevels, charlevels, sexlevels)	
charfviz <- makefvizdf(tissuelevels, charlevels, sexlevels)

@@

a <- plotcolorfulpcs(charpca,charpca$treatment, allcolors) + labs(subtitle = " ") +
  theme(legend.position = c(0.6,0.1), 
        legend.direction = "horizontal", 
        legend.key.size = unit(0.5, 'lines')) + 
  guides(color = FALSE) +
  labs(subtitle = " ")

b <- plotprolactin(PRLhyp, PRLhyp$counts, "PRL", "hypothalamus") + 
  theme(legend.position = c(0.7,0.9), axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.title.y = element_text(face = "italic"),
        legend.title = element_blank()) + guides(fill = F)

c <- plotfriz(charfviz) + labs(subtitle = "  ") +
  ylim(-250000,500000) + xlim(-250000,500000) + 
  theme(axis.text = element_blank())

d <- plotprolactin(PRLpit, PRLpit$counts, "PRL", "pituitary") + 
  theme(legend.position = "none", axis.text.x = element_blank(), axis.title.x = element_blank(),
        axis.title.y = element_text(face = "italic"))

e <- plotprolactin(prolactin, prolactin$plasma_conc, "prolactin (ng/mL)", "blood") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))

f <- plotprolactin(PRLgon, PRLgon$counts, "PRL", "gonads") + 
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(face = "italic"))

plot_grid(a,b,c,d,e,f, labels = "auto", ncol = 2, rel_heights = c(1,1,1.2))

>>>>

```{r data}
# pca
charpca <- subsetmakepca("pituitary", charlevels, sexlevels)	
charfviz <- makefvizdf("pituitary", charlevels, sexlevels)

@@

a <- plotcolorfulpcs(charpca,charpca$treatment, allcolors) + labs(subtitle = " ") +
  theme(legend.position = "none", 
        legend.direction = "horizontal", 
        legend.key.size = unit(0.5, 'lines')) + 
  guides(color = FALSE) +
  labs(subtitle = "pituitary")

b <- plotfriz(charfviz) + labs(subtitle = "pituitary") +
  #ylim(-250000,500000) + xlim(-250000,500000) + 
  theme(axis.text = element_blank())

c <- plotprolactin(PRLpit, PRLpit$counts, "PRL", "pituitary") + 
  theme(legend.position = "none", 
         axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(face = "italic"))

d <- plotprolactin(prolactin, prolactin$plasma_conc, "prolactin (ng/mL)", "blood") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))

abcd <- plot_grid(a,b,c,d, labels = c("b", "c", "d", "e"), ncol = 2, label_size = 8)

expdesign <- png::readPNG("../figures/images/parentalstages_fig1a.png")
expdesign <- ggdraw() +  draw_image(expdesign, scale = 1)

abcde <- plot_grid(expdesign, abcd, nrow = 2, labels = c("a", "b"), label_size = 8, rel_heights = c(0.3,1))
abcde
